\documentclass{letter}
% \usepackage[spanish]{babel}
% \usepackage[utf8]{inputenc}

\usepackage[margin=1in]{geometry}

\newcommand{\myName}{Arnoldo Del Toro}
\newcommand{\myDegree}{Master's degree in Engineering Systems and a Bachelor's degree in Mathematics}
\newcommand{\companyname}{AB Consulting}
\newcommand{\companyaddres}{Company address: \\ San Nicolás de los Garza, Nuevo León, 64000}


\begin{document}
\begin{letter}{ \companyname \\ \companyaddres}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the open position at your company. I am a recent graduate with a Master's degree in Engineering Systems and a Bachelor's degree in Mathematics. I have a keen interest in patterns, behavior, and data analysis with the aim of achieving data experimentation and prediction.

I consider myself a passionate person about knowledge, I believe that anyone can teach us something new. I think the best way to improve our skills is by teaching. Something I support is the use of {\bfseries effective} communication in both my personal and work life, which I try to improve every day. I prefer self-learning, however, I have no opposition when someone is willing to teach me. I love mathematics, it is incredible to be able to implement them in real problems. Even more, to achieve effective communication based on results, and/or generated information.

I am optimistic and fun in personal settings. In the workplace, I believe that the main factor to achieve a common goal is the correct tuning of responsibilities, in other words, briefly and effectively communicating requirements and responsibilities to each of the participants.

I look forward to the opportunity to further discuss how my background and skills would fit into your team. Thank you for considering my application.

\closing{Sincerely, \\ \myName}

\end{letter}
\end{document}

